Biologically-Constrained Error Correction for Connectome Reconstruction

### 2018-04-18 papers/quals2018/1_related_work.tex
quals: added first draft for qualifying exam proposals

\section{Related Work}
% \begin{figure}[t]
%  	\subfloat[]{
%  		\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
%  	}
%  	\subfloat[]{
%  		\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
%  	}
%  	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation. Red arrows highlight errors in the input segmentation. (b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
%  	\label{fig:improved-reconstruction}
% \end{figure}
%\\~\\
\noindent\textbf{Pixel-Based Segmentation}
%\subsubsection{Pixel-Based Segmentation}
A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
First, intermediate representations like boundary, affinity or binary segmentation maps are generated from voxels.
For the boundary probabilities, random forest with hand-designed features~\cite{kaynig2015large}, 2D and 3D convolution networks ~\cite{bogovic2013learned,seymour2016rhoananet,ronneberger2015u,ciresan2012deep,jain2010boundary,amelio_segmentation}.
Later, the affinity between each voxel and its six neighors are widely used~\cite{lee2015recursive,parag2017anisotropic,cciccek20163d,turaga2010convolutional,lee2017superhuman}. 3D U-Net architecture becomes popular~\cite{cciccek20163d} and MALIS cost function is designed to re-weight affinity prediction by their contribution to the segmentation error~\cite{briggman2009maximin}.
More recently, flood-filling networks~\cite{januszewski2016flood} produce binary segmentations from raw pixels with a recurrent convolution network at a high computational cost.
Orthogonal to the representation, model averaging~\cite{zeng2017deepem3d} and data augmentation~\cite{lee2017superhuman} methods can further improve the performance, where Lee et al.~\cite{lee2017superhuman} surpass the estimated human accuracy on the SNEMI3D dataset.

Then, clustering techniques transform these intermediate representations into segmentations.
Some early techniques apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
Often a watershed algorithm will then cluster these pixels into super-pixels~\cite{zlateski2015image}.
\\~\\
\noindent\textbf{Region Merging}
%\subsubsection{Region Merging}
Region merging methods can be categorized by the similarity metric between adjacent segments and the merging strategy.
For the similarity metric, Lee et al. and Funke et al. rely solely on the accuracy of the predicted affinities and define the metric as the mean affinity between segments~\cite{lee2017superhuman,funke2017deep}.
Classification-based method predicts the probability to merge two segments from handcrafted~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,jain2011learning} and learned features~\cite{bogovic2013learned}. 
For the merging stategy, most methods use variants of hierarchical agglomeration methods~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825} to greedily merge a pair of regions at a time.
Jain et al. formulates the agglomeration as a reinforcement learning problem ~\cite{jain2011learning} and Pape et al. present a scalable multicut algorithm to partition superpixels with global optimization~\cite{beier2017multicut}.
\\~\\
\noindent\textbf{Error-correction Methods}
 Additional research builds on top of these region-based methods to correct errors in the segmentation. This can be done either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. Our method can be used as input to any existing error correction framework.
% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.

>>>>

\section{Related Work}
% \begin{figure}[t]
%  	\subfloat[]{
%  		\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
%  	}
%  	\subfloat[]{
%  		\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
%  	}
%  	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation. Red arrows highlight errors in the input segmentation. (b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
%  	\label{fig:improved-reconstruction}
% \end{figure}
%\\~\\
\noindent\textbf{Pixel-Based Segmentation}
%\subsubsection{Pixel-Based Segmentation}
A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level of EM images.
First, intermediate representations like boundary, affinity or binary segmentation maps are generated from the voxels.
Random forests with hand-designed features~\cite{kaynig2015large}, or 2D and 3D convolutional networks produce boundary probabilities. ~\cite{seymour2016rhoananet,ronneberger2015u,bogovic2013learned,ciresan2012deep,jain2010boundary,amelio_segmentation}.
Often, the affinity between each voxel and its six neighbors are used~\cite{lee2015recursive,parag2017anisotropic,lee2017superhuman,cciccek20163d,turaga2010convolutional}. 
The 3D U-Net architecture has become popular~\cite{cciccek20163d} and the MALIS cost function is specifically designed to re-weight affinity predictions by their contribution to the segmentation error~\cite{briggman2009maximin}.
More recently, flood-filling networks~\cite{januszewski2016flood} produce binary segmentations from raw pixels with a recurrent convolutional network at a high computational cost.
Orthogonal to the representation, model averaging~\cite{zeng2017deepem3d} and data augmentation~\cite{lee2017superhuman} methods can further improve the performance, where Lee et al.~\cite{lee2017superhuman} surpass the estimated human accuracy on the SNEMI3D dataset.

Clustering techniques transform these intermediate representations into segmentations.
Some early methods apply computationally expensive graph partitioning algorithms with a single node per superpixel~\cite{andres2012globally}.
Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
Often a watershed algorithm will then cluster these pixels into super-pixels~\cite{zlateski2015image}.
\\~\\
\noindent\textbf{Region Merging}
%\subsubsection{Region Merging}
Region merging methods can be categorized by the similarity metric between adjacent segments and the merging strategy.
For the similarity metric, Lee et al. and Funke et al. rely solely on the accuracy of the predicted affinities and define the metric as the mean affinity between segments~\cite{lee2017superhuman,funke2017deep}.
Classification-based methods generate the probability to merge two segments from handcrafted~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825,jain2011learning} and learned features~\cite{bogovic2013learned}. 
For the merging strategy, most methods use variants of hierarchical agglomeration ~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825} to greedily merge a pair of regions at a time.
Jain et al. formulates the agglomeration problem as a reinforcement learning problem ~\cite{jain2011learning} and Pape et al. present a scalable multicut algorithm to partition superpixels with global optimization~\cite{beier2017multicut}.
\\~\\
\noindent\textbf{Error-correction Methods}
 Additional research builds on top of these region-based methods to correct errors in the segmentation. This can be done either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. Our method can be used as input to any existing error correction framework.
% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.

### 2018-04-18 papers/quals2018/4_results.tex
quals: added first draft for qualifying exam proposals

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
	\caption{Benchmark results on two datasets. We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph as the upper-bound for our method. Lower VI scores are better. Our method improves the segmentation accuracy over the baseline in all cases.
	Note that our model is only trained on Kasthuri dataset and it generalizes well on the FlyEM dataset.}
	\label{fig:variation-of-information}
\end{figure*}

>>>>

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
	\caption{Segmentation benchmark results on three volumes. We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method. Lower VI scores are better. Our method improves the segmentation accuracy over the baseline in all cases.
	Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
	\label{fig:variation-of-information}
\end{figure*}

### 2018-04-18 papers/quals2018/paper.tex
quals: added first draft for qualifying exam proposals

\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
%
\newcommand{\FIX}[1]{\textcolor{red}{#1}}
\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}

@@

	%%%%%%%%% TITLE
	\title{Graph-Based Neural Reconstruction from Skeletonized 3D Networks}
	% Neural Reconstruction Using Skeletonized 3D Networks
	% Neural Reconstruction with Top-Down Enhancements from Skeletonized 3D Networks
	% Graph-Based Neural Reconstruction from Morphological Skeletons
	%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}

	%\author{Brian Matejek\\
	%Harvard University\\
	%Cambridge, MA 02138, USA\\
	%{\tt\small bmatejek@seas.harvard.edu}
	%% For a paper whose authors are all at the same institution,
	%% omit the following lines up until the closing ``}''.
	%% Additional authors and addresses can be added with ``\and'',
	%% just like the second author.
	%% To save space, use either the email address or home page, not both
	%%\and
	%%Second Author\\
	%%Institution2\\
	%%First line of institution2 address\\
	%%{\tt\small secondauthor@i2.org}
	%}

@@

	%%%%%%%%% ABSTRACT
	\begin{abstract}
		Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
		Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
		However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
		In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
		We first generate skeletons in 3D from the neuron labels of the pixel-based segmentation.
		We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
		We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
		We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
		Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
		We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average split variation of information improvement of 19.3\%.
		%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
	\end{abstract}
	%%%%%%%%	% BODY TEXT

>>>>

\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
%

\cvprfinalcopy

@@

	%%%%%%%%% TITLE
	\title{Biologically-Constrained Error Correction for Connectome Reconstruction}

	\author{Brian Matejek\\
	Harvard University\\
	Cambridge, MA 02138, USA\\
	{\tt\small bmatejek@seas.harvard.edu}
	%% For a paper whose authors are all at the same institution,
	%% omit the following lines up until the closing ``}''.
	%% Additional authors and addresses can be added with ``\and'',
	%% just like the second author.
	%% To save space, use either the email address or home page, not both
	%%\and
	%%Second Author\\
	%%Institution2\\
	%%First line of institution2 address\\
	%%{\tt\small secondauthor@i2.org}
	}

@@

	%%%%%%%%% ABSTRACT
	\begin{abstract}
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
	\end{abstract}
	%%%%%%%%	% BODY TEXT
